---
title: "Fleet, reference table, documentation"
author: "Kirsten Birch Håkansson, DTU Aqua"
date: "\today"
output:
  pdf_document: default
---



```{r setup, include = F}
knitr::opts_chunk$set(echo = TRUE, message = F, warnings = F)

library(dplyr)
library(icesVocab)

options(scipen = 999)

path_in <- "Q:/50-radgivning/02-mynd/SAS Library/fleet/data/"
path_out <- "Q:/50-radgivning/02-mynd/SAS Library/fleet/" 
filename_out <- "fleet_old_metiers"

years <- c(2015:2024)
```


```{r data, eval = T}


# rdb <- read.csv("Q:/mynd/SAS Library/FiskeriAktiviteter/references/RDB/AreaCodeFACCodeRegion.csv")
# 
# #A bit of renaming and deletion of id's not needed presently
# 
# rdb <- select(rename(rdb, area = AreaCode, metier_lvl6 = FishingActivityCategoryEuropeanLvl6Code), area, metier_lvl6)

dfad <- readRDS(paste0(path_in, "metiers_exist_", min(years), "_", max(years),".rds"))

dfad_sum <- summarise(group_by(dfad, fao_area, merged_metier_level6, metier_level6_ret, fdfmark, target_spp_haul, art), 
                      kg = sum(kg), trips = sum(trips))

fleet <- dfad_sum

ic_fleets <- icesVocab::getCodeList("IC_FleetName")

```


# Data 

Input a list of all metiers used `r min(dfad$year)`-`r max(dfad$year)` in the data. 

# Check merged_metier_level6

merged_metier_level6 is used as input to the code. 
This is already a re-coded of the old

```{r}

diff <- subset(fleet, merged_metier_level6 != metier_level6_ret & 
                 !(metier_level6_ret %in% c("No_logbook6_>10", "No_logbook6",
                                          "No_Matrix6")) &
                 substr(merged_metier_level6, 5, 7) != "MCD")

```

# Check 

# mixfish_fleet


Also need a mixfish_fleet for saithe, haddock and cod

The fleet are in principal coded from Q:/mynd/SAS Library/fleet/references/Fisheries_Data_call 2023_CoverLetter&Text_v2.pdf, if not this is mentioned below.

```{r}

mix <-
  mutate(
    fleet,
    metier_in = ifelse(
      is.na(merged_metier_level6) | merged_metier_level6 == "",
      metier_level6_ret ,
      merged_metier_level6
    )
  )

# 27.3.a ----

# DRB_MOL
mix$mixfish_fleet[mix$fao_area %in% c("27.3.a.20", "27.3.a.21") &
                    mix$metier_in == "DRB_MOL_>=0_0_0"] <- "DRB_MOL_0_0_0_all"
#Above, This is not according to the annex, since I have stolen the fleet from another area
#In the past we would probably not have submitted this fleet, since it normally don't catch
#stocks under WGNSSK & MIXFISH. It has been included, since we now include all effort.

# TBB
mix$mixfish_fleet[mix$fao_area %in% c("27.3.a.20", "27.3.a.21") &
                    mix$metier_in == "TBB_CRU_16-31_0_0"] <- "TBB_CRU_16-31_0_0_all"
mix$mixfish_fleet[mix$fao_area %in% c("27.3.a.20", "27.3.a.21") &
                    mix$metier_in %in% c("TBB_DEF_90-99_0_0", "TBB_DEF_90-119_0_0")] <- "TBB_DEF_90-99_0_0_all"
#Above - I would like to remove TBB_DEF_90-119_0_0 from this
mix$mixfish_fleet[mix$fao_area %in% c("27.3.a.20", "27.3.a.21") &
                    mix$metier_in == "TBB_DEF_>=120_0_0"] <- "TBB_DEF_>=120_0_0_all"

#OTB
mix$mixfish_fleet[mix$fao_area %in% c("27.3.a.20", "27.3.a.21") &
                    mix$metier_in == "OTB_CRU_16-31_0_0"] <- "OTB_CRU_16-31_0_0_all"
mix$mixfish_fleet[mix$fao_area %in% c("27.3.a.20", "27.3.a.21") &
                    mix$metier_in == "OTB_CRU_32-69_0_0"] <- "OTB_CRU_32-69_0_0_all"
mix$mixfish_fleet[mix$fao_area %in% c("27.3.a.20", "27.3.a.21") &
                    mix$metier_in == "OTB_MCD_90-119_0_0"] <- "OTB_CRU_90-119_0_0_all"
mix$mixfish_fleet[mix$fao_area %in% c("27.3.a.20", "27.3.a.21") &
                    mix$metier_in == "OTB_MCD_>=120_0_0"] <- "OTB_DEF_>=120_0_0_all"
mix$mixfish_fleet[mix$fao_area %in% c("27.3.a.20", "27.3.a.21") &
                    mix$metier_in == "OTB_CRU_70-89_2_35"] <- "OTB_CRU_70-89_2_35_all"

#OTM
mix$mixfish_fleet[mix$fao_area %in% c("27.3.a.20", "27.3.a.21") &
                    mix$metier_in == "OTM_SPF_32-69_0_0"] <- "OTM_SPF_32-69_0_0_all"

# PS
mix$mixfish_fleet[mix$fao_area %in% c("27.3.a.20", "27.3.a.21") &
                    substr(mix$metier_in, 1, 2) == "PS"] <- "PS"
#Above, This is not according to the annex, since I have stolen the fleet from another AWG.
#The fleet is not in the MIXFISH list
#In the past we would probably not have submitted this fleet, since it normally don't catch
#stocks under WGNSSK & MIXFISH. It has been included, since we now include all effort.
#In 27.3.a PS_SPF_32-69_0_0 was set to OTB_SPF_32-69_0_0

#SDN & SSC
mix$mixfish_fleet[mix$fao_area %in% c("27.3.a.20", "27.3.a.21") &
                    mix$metier_in %in% c("SDN_DEF_90-119_0_0", "SDN_DEF_>=120_0_0")] <- "SDN_DEF_>=120_0_0_all"
#Above - I would like to remove SDN_DEF_90-119_0_0 from this, when we decided on this the fleet was insignificant.
#This has changed
mix$mixfish_fleet[mix$fao_area %in% c("27.3.a.20", "27.3.a.21") &
                    mix$metier_in %in% c("SSC_DEF_90-119_0_0", "SSC_DEF_>=120_0_0")] <- "SSC_DEF_>=120_0_0_all"
#Above - I would like to remove SSC_DEF_90-119_0_0 from this, when we decided on this the fleet was insignificant.
#This has maybe changed

#GNS & LLS
mix$mixfish_fleet[mix$fao_area %in% c("27.3.a.20", "27.3.a.21") &
                    mix$metier_in == "GNS_DEF_100-119_0_0"] <- "GNS_DEF_100-119_0_0_all"
mix$mixfish_fleet[mix$fao_area %in% c("27.3.a.20", "27.3.a.21") &
                    mix$metier_in == "GNS_DEF_120-219_0_0"] <- "GNS_DEF_120-219_0_0_all"
mix$mixfish_fleet[mix$fao_area %in% c("27.3.a.20", "27.3.a.21") &
                    mix$metier_in == "GNS_DEF_>=220_0_0"] <- "GNS_DEF_>=220_0_0_all"

# LLS
mix$mixfish_fleet[mix$fao_area %in% c("27.3.a.20", "27.3.a.21") &
                    substr(mix$metier_in, 1, 3) == "LLS"] <- "LLS_FIF_0_0_0_all"

# IBC
mix$mixfish_fleet[mix$fao_area %in% c("27.3.a.20", "27.3.a.21") &
                    mix$metier_in %in% c("OTM_SPF_16-31_0_0",
                                         "OTB_SPF_>=120_0_0",
                                         "OTB_DEF_16-31_0_0",
                                         "OTB_DEF_<16_0_0")] <- "MIS_MIS_0_0_0_IBC"
# All other
mix$mixfish_fleet[mix$fao_area %in% c("27.3.a.20", "27.3.a.21") &
                    substr(mix$metier_in, 1, 3) == "No_"] <- "MIS_MIS_0_0_0_HC"
mix$mixfish_fleet[mix$fao_area %in% c("27.3.a.20", "27.3.a.21") &
                    is.na(mix$mixfish_fleet)] <- "MIS_MIS_0_0_0_HC"

# 27.7.d ----
# TBB
mix$mixfish_fleet[mix$fao_area %in% c("27.7.d") &
                    mix$metier_in == "TBB_CRU_16-31_0_0"] <- "TBB_CRU_16-31_0_0_all"
mix$mixfish_fleet[mix$fao_area %in% c("27.7.d") &
                    mix$metier_in == "TBB_CRU_70-99_0_0"] <- "TBB_CRU_70-99_0_0_all"
mix$mixfish_fleet[mix$fao_area %in% c("27.7.d") &
                    mix$metier_in == "TBB_DEF_>=120_0_0"] <- "TBB_DEF_>=120_0_0_all"

# OTB
mix$mixfish_fleet[mix$fao_area %in% c("27.7.d") &
                    mix$metier_in == "OTB_CRU_16-31_0_0"] <- "OTB_CRU_16-31_0_0_all"
mix$mixfish_fleet[mix$fao_area %in% c("27.7.d") &
                    mix$metier_in == "OTB_CRU_32-69_0_0"] <- "OTB_CRU_32-69_0_0_all"
mix$mixfish_fleet[mix$fao_area %in% c("27.7.d") &
                    mix$metier_in == "OTB_DEF_32-69_0_0"] <- "OTB_DEF_32-69_0_0_all"
#Above, Data from 1987-2024. This is a Norway Pout fishery. So we catch NOP in area 27.7.d?
mix$mixfish_fleet[mix$fao_area %in% c("27.7.d") &
                    mix$metier_in == "OTB_MCD_70-99_0_0"] <- "OTB_CRU_70-99_0_0_all"
mix$mixfish_fleet[mix$fao_area %in% c("27.7.d") &
                    mix$metier_in == "OTB_MCD_100-119_0_0"] <- "OTB_DEF_100-119_0_0_all"
#Above, check - this is not according to the annex, since I have stolen the fleet from another area.
#Maybe this could be split into CRU / DEF instead of hardcoding.
mix$mixfish_fleet[mix$fao_area %in% c("27.7.d") &
                    mix$metier_in == "OTB_MCD_>=120_0_0"] <- "OTB_DEF_>=120_0_0_all"

# IBC
mix$mixfish_fleet[mix$fao_area %in% c("27.7.d") &
                    mix$metier_in %in% c("OTM_SPF_16-31_0_0",
                                         "OTB_SPF_>=120_0_0",
                                         "OTB_DEF_16-31_0_0")] <- "MIS_MIS_0_0_0_IBC"
#Above, Data from 1987-2024. OTB_SPF_>=120_0_0 is trips with 999 in mesh and catching PIL and BRS

# SPF_32-69
mix$mixfish_fleet[mix$fao_area %in% c("27.7.d") &
                    mix$metier_in == "OTM_SPF_32-69_0_0"] <- "OTM_SPF_32-69_0_0_all"
#Above, This is not according to the annex, since I have stolen the fleet from another area

# LLS
mix$mixfish_fleet[mix$fao_area %in% c("27.7.d") &
                    substr(mix$metier_in, 1, 3) == "LLS"] <- "LLS_FIF_0_0_0_all"

# GNS
mix$mixfish_fleet[mix$fao_area %in% c("27.7.d") &
                    mix$metier_in == "GNS_DEF_100-119_0_0"] <- "GNS_DEF_100-119_0_0_all"
mix$mixfish_fleet[mix$fao_area %in% c("27.7.d") &
                    mix$metier_in == "GNS_DEF_120-219_0_0"] <- "GNS_DEF_120-219_0_0_all"
mix$mixfish_fleet[mix$fao_area %in% c("27.7.d") &
                    mix$metier_in == "GNS_DEF_>=220_0_0"] <- "GNS_DEF_>=220_0_0_all"

# All other
mix$mixfish_fleet[mix$fao_area %in% c("27.7.d") &
                    mix$metier_in == "No_Matrix6"] <- "MIS_MIS_0_0_0_HC"
#Above, data from 1987-2024. This is a bit rough, but for most of the data it is True. There are two BRS / PIL trips that get this one

# 27.4 & 27.6.a ----

areas <- c("27.4.a", "27.4.b", "27.4.c", "27.6.a")

# TBB
mix$mixfish_fleet[mix$fao_area %in% areas &
                    mix$metier_in == "TBB_CRU_16-31_0_0"] <- "TBB_CRU_16-31_0_0_all"
mix$mixfish_fleet[mix$fao_area %in% areas &
                    mix$metier_in %in% c("TBB_CRU_70-99_0_0", "TBB_DEF_70-99_0_0")] <- "TBB_DEF_70-99_0_0_all"
mix$mixfish_fleet[mix$fao_area %in% areas &
                    mix$metier_in == "TBB_DEF_>=120_0_0"] <- "TBB_DEF_>=120_0_0_all"

# OTB
mix$mixfish_fleet[mix$fao_area %in% areas &
                    mix$metier_in == "OTB_CRU_16-31_0_0"] <- "OTB_CRU_16-31_0_0_all"
mix$mixfish_fleet[mix$fao_area %in% areas &
                    mix$metier_in == "OTB_CRU_32-69_0_0"] <- "OTB_CRU_32-69_0_0_all"
mix$mixfish_fleet[mix$fao_area %in% areas &
                    mix$metier_in == "OTB_DEF_32-69_0_0"] <- "OTB_DEF_32-69_0_0_all"
mix$mixfish_fleet[mix$fao_area %in% areas &
                    mix$metier_in == "OTB_MCD_70-99_0_0"] <- "OTB_CRU_70-99_0_0_all"
mix$mixfish_fleet[mix$fao_area %in% areas &
                    mix$metier_in == "OTB_MCD_100-119_0_0"] <- "OTB_DEF_100-119_0_0_all"
mix$mixfish_fleet[mix$fao_area %in% areas &
                    mix$metier_in == "OTB_MCD_>=120_0_0"] <- "OTB_DEF_>=120_0_0_all"

# SDN
mix$mixfish_fleet[mix$fao_area %in% areas &
                    mix$metier_in %in% c("SDN_DEF_>=120_0_0")] <- "SDN_DEF_>=120_0_0_all"
mix$mixfish_fleet[mix$fao_area %in% areas &
                    mix$metier_in %in% c("SDN_DEF_100-119_0_0")] <- "SDN_DEF_100-119_0_0_all"
#Above, not sure SDN_DEF_100-119_0_0 is a mixfish fleet in the North sea, but the code is in the vocab
#Before these two metiers were joined in >=120

# SSC
mix$mixfish_fleet[mix$fao_area %in% areas &
                    mix$metier_in %in% c("SSC_DEF_>=120_0_0")] <- "SSC_DEF_>=120_0_0_all"
mix$mixfish_fleet[mix$fao_area %in% areas &
                    mix$metier_in %in% c("SSC_DEF_100-119_0_0")] <- "SSC_DEF_100-119_0_0_all"
#Above, not sure SDN_DEF_100-119_0_0 is a mixfish fleet in the North sea, but the code is in the vocab

# GNS
mix$mixfish_fleet[mix$fao_area %in% areas &
                    mix$metier_in == "GNS_DEF_90-99_0_0"] <- "GNS_DEF_90-99_0_0_all"
mix$mixfish_fleet[mix$fao_area %in% areas &
                    mix$metier_in == "GNS_DEF_100-119_0_0"] <- "GNS_DEF_100-119_0_0_all"
mix$mixfish_fleet[mix$fao_area %in% areas &
                    mix$metier_in == "GNS_DEF_120-219_0_0"] <- "GNS_DEF_120-219_0_0_all"
mix$mixfish_fleet[mix$fao_area %in% areas &
                    mix$metier_in == "GNS_DEF_>=220_0_0"] <- "GNS_DEF_>=220_0_0_all"

# LLS
mix$mixfish_fleet[mix$fao_area %in% areas &
                    substr(mix$metier_in, 1, 3) == "LLS"] <- "LLS_FIF_0_0_0_all"

# FPO
mix$mixfish_fleet[mix$fao_area %in% areas &
                    mix$metier_in == "FPO_CRU_>0_0_0"] <- "FPO_CRU_0_0_0_all"

# SPF_32-69
mix$mixfish_fleet[mix$fao_area %in% areas &
                    mix$metier_in == "OTM_SPF_32-69_0_0"] <- "OTM_SPF_32-69_0_0_all"
#Above, This is not according to the annex, since I have stolen the fleet from another area
#In the past we would probably not have submitted this fleet, since it normally don't catch
#stocks under WGNSSK & MIXFISH. It has been included, since we now include all effort.

# IBC
mix$mixfish_fleet[mix$fao_area %in% areas &
                    mix$metier_in %in% c(
                      "OTM_SPF_16-31_0_0",
                      "OTB_DEF_<16_0_0",
                      "OTB_DEF_16-31_0_0",
                      "OTB_SPF_>=120_0_0",
                      "OTM_SPF_>=120_0_0"
                    )] <- "MIS_MIS_0_0_0_IBC"
#Above, data from 1987-2024. SPF_>=120_0_0 is trips mainly with 999 in mesh and catching SPF
#OTB_SPF_>=120_0_0 & OTM_SPF_>=120_0_0 are mainly from unsorted fisheries

# DRB_MOL
mix$mixfish_fleet[mix$fao_area %in% areas &
                    mix$metier_in == "DRB_MOL_>=0_0_0"] <- "DRB_MOL_0_0_0_all"
#Above, This is not according to the annex, since I have stolen the fleet from another area
#In the past we would probably not have submitted this fleet, since it normally don't catch
#stocks under WGNSSK & MIXFISH. It has been included, since we now include all effort.


# PS
mix$mixfish_fleet[mix$fao_area %in% areas &
                    substr(mix$metier_in, 1, 2) == "PS"] <- "PS"
#Above, This is not according to the annex, since I have stolen the fleet from another AWG.
#The fleet is not in the MIXFISH list
#In the past we would probably not have submitted this fleet, since it normally don't catch
#stocks under WGNSSK & MIXFISH. It has been included, since we now include all effort.


# All other
mix$mixfish_fleet[mix$fao_area %in% areas &
                    substr(mix$metier_in, 1, 3) == "No_"] <- "MIS_MIS_0_0_0_HC"
mix$mixfish_fleet[mix$fao_area %in% areas &
                    is.na(mix$mixfish_fleet)] <- "MIS_MIS_0_0_0_HC"




test_7d <-
  summarise(
    group_by(
      subset(mix, fao_area %in% c("27.7.d")),
      merged_metier_level6,
      metier_level6_ret,
      mixfish_fleet
    ),
    kg = sum(kg),
    trips = sum(trips)
  )

test_46a <-
  summarise(
    group_by(
      subset(mix, fao_area %in% areas),
      merged_metier_level6,
      metier_level6_ret,
      mixfish_fleet
    ),
    kg = sum(kg),
    trips = sum(trips)
  )

test_3a <-
  summarise(
    group_by(
      subset(mix, fao_area %in% c("27.3.a.20", "27.3.a.21")),
      merged_metier_level6,
      metier_level6_ret,
      mixfish_fleet
    ),
    kg = sum(kg),
    trips = sum(trips)
  )

# mark fdf
fdf <- mix
unique(fdf$fdfmark)

fdf$mixfish_fleet[fdf$fdfmark == "FDF" & fdf$mixfish_fleet %in% c("OTB_CRU_90-119_0_0_all")] <- "OTB_CRU_90-119_0_0_all_FDF"
fdf$mixfish_fleet[fdf$fdfmark == "FDF" & fdf$mixfish_fleet %in% c("OTB_DEF_>=120_0_0_all")] <- "OTB_DEF_>=120_0_0_all_FDF"



# Slut
fleet <- ungroup(fdf)

# rm(mix, mix_1)




```

# wgbfas_dem_effort_fleet

```{r}

areas <- c("27.3.a.20", "27.3.a.21", "27.3.b.23", "27.3.c.22", "27.3.d.24",
           "27.3.d.25", "27.3.d.26", "27.3.d.27", "27.3.d.28", "27.3.d.29",
           "27.3.d.30", "27.3.d.31", "27.3.d.32", "27.3.d.28.1", "27.3.d.28.2")

huc <- fleet
huc$wgbfas_dem_effort_fleet <- NA

huc$wgbfas_dem_effort_fleet[huc$fao_area %in% areas &
                              substr(huc$merged_metier_level6,1,3) %in% c('FPN','GNS','LHP','LLS','FPO','FYK','GND','LLD') &
                              substr(huc$merged_metier_level6,5,7) %in% c('DEF','MCD') 
                            ] <- "Passive"

huc$wgbfas_dem_effort_fleet[huc$metier_level6_ret == "No_logbook6"] <- "Passive"

huc$wgbfas_dem_effort_fleet[huc$fao_area %in% areas &
                              substr(huc$merged_metier_level6,1,3) %in% c('OTB', "SDN", "SSC") &
                              substr(huc$merged_metier_level6,5,7) %in% c('DEF','MCD',"CRU") 
                            ] <- "Active"

huc$wgbfas_dem_effort_fleet[huc$fao_area %in% areas &
                    huc$merged_metier_level6 %in% c("OTM_SPF_16-31_0_0",
                                         "OTB_DEF_16-31_0_0",
                                         "OTB_DEF_<16_0_0",
                                         "OTM_SPF_16-104_0_0")] <- "MIS_MIS_0_0_0_IBC"
# "OTM_SPF_16-104_0_0" is the period 2015-2024 by a large majority from <32mm

fleet <- ungroup(huc)
```

## Test wgbfas fleets
```{r}

dfad$stock <- NA
dfad$stock[dfad$art == "ISG" & dfad$fao_area %in% c("27.3.b.23", "27.3.c.22", "27.3.d.24",
           "27.3.d.25", "27.3.d.26", "27.3.d.27", "27.3.d.28", "27.3.d.29",
           "27.3.d.30", "27.3.d.31", "27.3.d.32", "27.3.d.28.1", "27.3.d.28.2")] <- "dab.27.22-32"
  
dfad$stock[dfad$art == "PGH" & dfad$fao_area %in% c("27.3.b.23", "27.3.c.22", "27.3.d.24",
           "27.3.d.25", "27.3.d.26", "27.3.d.27", "27.3.d.28", "27.3.d.29",
           "27.3.d.30", "27.3.d.31", "27.3.d.32", "27.3.d.28.1", "27.3.d.28.2")] <- "tur.27.22-32"

dfad$stock[dfad$art == "SLH" & dfad$fao_area %in% c("27.3.b.23", "27.3.c.22", "27.3.d.24",
           "27.3.d.25", "27.3.d.26", "27.3.d.27", "27.3.d.28", "27.3.d.29",
           "27.3.d.30", "27.3.d.31", "27.3.d.32", "27.3.d.28.1", "27.3.d.28.2")] <- "bll.27.22-32"

dfad$stock[dfad$art == "RSP" & dfad$fao_area %in% c("27.3.a.21", "27.3.b.23", "27.3.c.22")] <- "ple.27.21-23"

dfad$stock[dfad$art == "RSP" & dfad$fao_area %in% c("27.3.d.24",
           "27.3.d.25", "27.3.d.26", "27.3.d.27", "27.3.d.28", "27.3.d.29",
           "27.3.d.30", "27.3.d.31", "27.3.d.32", "27.3.d.28.1", "27.3.d.28.2")] <- "ple.27.24-32"

dfad$stock[dfad$art == "TOR" & dfad$fao_area %in% c("27.3.a.21")] <- "cod.27.21"

dfad$stock[dfad$art == "TOR" & dfad$fao_area %in% c("27.3.b.23", "27.3.c.22", "27.3.d.24")] <- "cod.27.22-24"

dfad$stock[dfad$art == "TOR" & dfad$fao_area %in% c(
           "27.3.d.25", "27.3.d.26", "27.3.d.27", "27.3.d.28", "27.3.d.29",
           "27.3.d.30", "27.3.d.31", "27.3.d.32", "27.3.d.28.1", "27.3.d.28.2")] <- "cod.27.24-32"

dfad$stock[dfad$art == "TNG" & dfad$fao_area %in% c("27.3.a.20", "27.3.a.21", "27.3.b.23", "27.3.c.22", "27.3.d.24",
           "27.3.d.25", "27.3.d.26", "27.3.d.27", "27.3.d.28", "27.3.d.29",
           "27.3.d.30", "27.3.d.31", "27.3.d.32", "27.3.d.28.1", "27.3.d.28.2")] <- "sol.27.20-24"

dfad$stock[dfad$art == "SKR" & dfad$fao_area %in% c("27.3.b.23", "27.3.c.22")] <- "fle.27.2223"

dfad$stock[dfad$art == "SKR" & dfad$fao_area %in% c("27.3.d.24",
           "27.3.d.25")] <- "bzq.27.2425"

dfad$stock[dfad$art == "SKR" & dfad$fao_area %in% c("27.3.d.26", "27.3.d.27", "27.3.d.28", "27.3.d.28.1", "27.3.d.28.2")] <- "bzq.27.2628"

dfad_stock <- subset(dfad, !is.na(stock) & year == 2024)

wgbfas_dem_effort_fleet <- distinct(fleet, metier_level6_ret, fao_area, wgbfas_dem_effort_fleet)

dfad_stock_fleet <- left_join(dfad_stock, wgbfas_dem_effort_fleet)

test_wgbfas <-
  summarise(
    group_by(
      dfad_stock_fleet,
      merged_metier_level6,
      metier_level6_ret,
      wgbfas_dem_effort_fleet,
      stock
    ),
    kg = sum(kg)
  )

test_wgbfas <- arrange(test_wgbfas, stock, -kg)
test_wgbfas <- mutate(group_by(test_wgbfas, stock), sumcum = cumsum(kg)/sum(kg))

write.csv(test_wgbfas, paste0(path_out, "test_wgbfas_2024.csv"), row.names = F)

dfad_stock <- subset(dfad, !is.na(stock))

wgbfas_dem_effort_fleet <- distinct(fleet, metier_level6_ret, fao_area, wgbfas_dem_effort_fleet)

dfad_stock_fleet <- left_join(dfad_stock, wgbfas_dem_effort_fleet)

test_wgbfas <-
  summarise(
    group_by(
      dfad_stock_fleet,
      merged_metier_level6,
      metier_level6_ret,
      wgbfas_dem_effort_fleet,
      stock
    ),
    kg = sum(kg)
  )

test_wgbfas <- arrange(test_wgbfas, stock, -kg)
test_wgbfas <- mutate(group_by(test_wgbfas, stock), sumcum = cumsum(kg)/sum(kg))

write.csv(test_wgbfas, paste0(path_out, "test_wgbfas_2015_2024.csv"), row.names = F)
```

## What is "OTM_SPF_16-104_0_0"
```{r}
otm <- subset(dfad, merged_metier_level6 == "OTM_SPF_16-104_0_0")
```


```{r output, include = T}

matrix_out <-
  distinct(
    ungroup(fleet),
    fao_area,
    metier_level6_ret,
    fdfmark,
    # obs_at_sea_fleets_no_gns,
    # obs_at_sea_fleets_gns,
    # merged_metier_level6,
    mixfish_fleet,
    wgbfas_dem_effort_fleet
  )

matrix_out

# matrix_out <- rename(matrix_out, metier_level6 = metier_level6_ret)

saveRDS(matrix_out, paste0(path_out, filename_out, ".rds"))
write.csv(matrix_out, paste0(path_out, filename_out, ".csv"), row.names = F)

```


