---
title: "Fleet, reference table, documentation"
author: "Kirsten Birch Håkansson, DTU Aqua"
date: "\today"
output:
  pdf_document: default
---



```{r setup, include = F}
knitr::opts_chunk$set(echo = TRUE, message = F, warnings = F)

library(dplyr)

options(scipen = 999)

path_in <- "Q:/50-radgivning/02-mynd/SAS Library/fleet/data/"
path_out <- "Q:/50-radgivning/02-mynd/SAS Library/fleet/" 
filename_out <- "fleet_old_metiers"

years <- c(2015:2024)
```


```{r data, eval = T}


# rdb <- read.csv("Q:/mynd/SAS Library/FiskeriAktiviteter/references/RDB/AreaCodeFACCodeRegion.csv")
# 
# #A bit of renaming and deletion of id's not needed presently
# 
# rdb <- select(rename(rdb, area = AreaCode, metier_lvl6 = FishingActivityCategoryEuropeanLvl6Code), area, metier_lvl6)

dfad <- readRDS(paste0(path_in, "metiers_exist_", min(years), "_", max(years),".rds"))

dfad_sum <- summarise(group_by(dfad, fao_area, merged_metier_level6, metier_level6_ret, target_spp_haul), 
                      kg = sum(kg), trips = sum(trips))

fleet <- dfad_sum

```


# Data 

Input a list of all metiers used `r min(dfad$year)`-`r max(dfad$year)` in the data. 

# Check merged_metier_level6

merged_metier_level6 is used as input to the code. 
This is already a re-coded of the old

```{r}

diff <- subset(fleet, merged_metier_level6 != metier_level6_ret & 
                 !(metier_level6_ret %in% c("No_logbook6_>10", "No_logbook6",
                                          "No_Matrix6")) &
                 substr(merged_metier_level6, 5, 7) != "MCD")

```

# Check 

# mixfish_fleet


Also need a mixfish_fleet for saithe, haddock and cod

The fleet are in principal coded from Q:/mynd/SAS Library/fleet/references/Fisheries_Data_call 2023_CoverLetter&Text_v2.pdf, if not this is mentioned below.

```{r}

mix <-
  mutate(
    fleet,
    metier_in = ifelse(
      is.na(merged_metier_level6) | merged_metier_level6 == "",
      metier_level6_ret ,
      merged_metier_level6
    )
  )

mix_1 <- c()

for (i in (1:nrow(mix))) {
  mixi <- mix[i, ]

 # 27.3.a
  if (mixi$fao_area %in% c("27.3.a.20", "27.3.a.21")) {
    # TBB
    mixi$mixfish_fleet[mixi$metier_in == "TBB_CRU_16-31_0_0"] <- "TBB_CRU_16-31_0_0_all"
    mixi$mixfish_fleet[mixi$metier_in %in% c("TBB_DEF_90-99_0_0", "TBB_DEF_90-119_0_0")] <- "TBB_DEF_90-99_0_0_all"
    #Above - I would like to remove TBB_DEF_90-119_0_0 from this
    mixi$mixfish_fleet[mixi$metier_in == "TBB_DEF_>=120_0_0"] <- "TBB_DEF_>=120_0_0_all"

    #OTB
    mixi$mixfish_fleet[mixi$metier_in == "OTB_CRU_16-31_0_0"] <- "OTB_CRU_16-31_0_0_all"
    mixi$mixfish_fleet[mixi$metier_in == "OTB_CRU_32-69_0_0"] <- "OTB_CRU_32-69_0_0_all"
    mixi$mixfish_fleet[mixi$metier_in == "OTB_MCD_90-119_0_0"] <- "OTB_CRU_90-119_0_0_all"
    mixi$mixfish_fleet[mixi$metier_in == "OTB_MCD_>=120_0_0"] <- "OTB_DEF_>=120_0_0"
    mixi$mixfish_fleet[mixi$metier_in == "OTB_CRU_70-89_2_35"] <- "OTB_CRU_70-89_2_35_all"
    
    #OTM
    mixi$mixfish_fleet[mixi$metier_in == "OTM_SPF_32-69_0_0"] <- "OTM_SPF_32-69_0_0_all"
    
    # PS
    mixi$mixfish_fleet[substr(mixi$metier_in, 1, 2) == "PS"] <- "PS"
    #Above, This is not according to the annex, since I have stolen the fleet from another AWG.
    #The fleet is not in the MIXFISH list
    #In the past we would probably not have submitted this fleet, since it normally don't catch
    #stocks under WGNSSK & MIXFISH. It has been included, since we now include all effort. 
    #In 27.3.a PS_SPF_32-69_0_0 was set to OTB_SPF_32-69_0_0
               
    #SDN & SSC
    mixi$mixfish_fleet[mixi$metier_in %in% c("SDN_DEF_90-119_0_0", "SDN_DEF_>=120_0_0")] <- "SDN_DEF_>=120_0_0_all"
    #Above - I would like to remove SDN_DEF_90-119_0_0 from this, when we decided on this the fleet was insignificant.
    #This has changed
    mixi$mixfish_fleet[mixi$metier_in %in% c("SSC_DEF_90-119_0_0", "SSC_DEF_>=120_0_0")] <- "SSC_DEF_>=120_0_0_all"
    #Above - I would like to remove SSC_DEF_90-119_0_0 from this, when we decided on this the fleet was insignificant.
    #This has maybe changed
    
    #GNS & LLS
    mixi$mixfish_fleet[mixi$metier_in == "GNS_DEF_100-119_0_0"] <- "GNS_DEF_100-119_0_0_all"
    mixi$mixfish_fleet[mixi$metier_in == "GNS_DEF_120-219_0_0"] <- "GNS_DEF_120-219_0_0_all"
    mixi$mixfish_fleet[mixi$metier_in == "GNS_DEF_>=220_0_0"] <- "GNS_DEF_>=220_0_0_all"
    
    # LLS
    mixi$mixfish_fleet[substr(mixi$metier_in, 1, 3) == "LLS"] <- "LLS_FIF_0_0_0_all"
    
    # IBC
    mixi$mixfish_fleet[mixi$metier_in %in% c("OTM_SPF_16-31_0_0",
                                             "OTB_SPF_>=120_0_0",
                                             "OTB_DEF_16-31_0_0")] <- "MIS_MIS_0_0_0_IBC"

  }
  # 27.7.d ----
  else if (mixi$fao_area %in% c("27.7.d")) {
    # TBB
    mixi$mixfish_fleet[mixi$metier_in == "TBB_CRU_16-31_0_0"] <- "TBB_CRU_16-31_0_0_all"
    mixi$mixfish_fleet[mixi$metier_in == "TBB_CRU_70-99_0_0"] <- "TBB_CRU_70-99_0_0_all"
    mixi$mixfish_fleet[mixi$metier_in == "TBB_DEF_>=120_0_0"] <- "TBB_DEF_>=120_0_0_all"

    # OTB
    mixi$mixfish_fleet[mixi$metier_in == "OTB_CRU_16-31_0_0"] <- "OTB_CRU_16-31_0_0_all"
    mixi$mixfish_fleet[mixi$metier_in == "OTB_CRU_32-69_0_0"] <- "OTB_CRU_32-69_0_0_all"
    mixi$mixfish_fleet[mixi$metier_in == "OTB_DEF_32-69_0_0"] <- "OTB_DEF_32-69_0_0_all"
    #Above, Data from 1987-2024. This is a Norway Pout fishery. So we catch NOP in area 27.7.d?
    mixi$mixfish_fleet[mixi$metier_in == "OTB_MCD_70-99_0_0"] <- "OTB_CRU_70-99_0_0_all"
    mixi$mixfish_fleet[mixi$metier_in == "OTB_MCD_100-119_0_0"] <- "OTB_DEF_100-119_0_0_all"
    #Above, check - this is not according to the annex, since I have stolen the fleet from another area.
    #Maybe this could be split into CRU / DEF instead of hardcoding.
    mixi$mixfish_fleet[mixi$metier_in == "OTB_MCD_>=120_0_0"] <- "OTB_DEF_>=120_0_0_all"

    # IBC
    mixi$mixfish_fleet[mixi$metier_in %in% c("OTM_SPF_16-31_0_0",
                                             "OTB_SPF_>=120_0_0",
                                             "OTB_DEF_16-31_0_0")] <- "MIS_MIS_0_0_0_IBC"
    #Above, Data from 1987-2024. OTB_SPF_>=120_0_0 is trips with 999 in mesh and catching PIL and BRS

    # SPF_32-69
    mixi$mixfish_fleet[mixi$metier_in == "OTM_SPF_32-69_0_0"] <- "OTM_SPF_32-69_0_0_all"
    #Above, This is not according to the annex, since I have stolen the fleet from another area

    # LLS
    mixi$mixfish_fleet[substr(mixi$metier_in, 1, 3) == "LLS"] <- "LLS_FIF_0_0_0_all"

    # GNS
    mixi$mixfish_fleet[mixi$metier_in == "GNS_DEF_100-119_0_0"] <- "GNS_DEF_100-119_0_0_all"
    mixi$mixfish_fleet[mixi$metier_in == "GNS_DEF_120-219_0_0"] <- "GNS_DEF_120-219_0_0_all"
    mixi$mixfish_fleet[mixi$metier_in == "GNS_DEF_>=220_0_0"] <- "GNS_DEF_>=220_0_0_all"

    # All other
    mixi$mixfish_fleet[mixi$metier_in == "No_Matrix6"] <- "MIS_MIS_0_0_0_HC"
    #Above, data from 1987-2024. This is a bit rough, but for most of the data it is True. There are two BRS / PIL trips that get this one

  }
  # 27.4 ----
  else if (mixi$fao_area %in% c("27.4.a", "27.4.b", "27.4.c")) {

    # TBB
    mixi$mixfish_fleet[mixi$metier_in == "TBB_CRU_16-31_0_0"] <- "TBB_CRU_16-31_0_0_all"
    mixi$mixfish_fleet[mixi$metier_in %in% c("TBB_CRU_70-99_0_0", "TBB_DEF_70-99_0_0")] <- "TBB_DEF_70-99_0_0_all"
    mixi$mixfish_fleet[mixi$metier_in == "TBB_DEF_>=120_0_0"] <- "TBB_DEF_>=120_0_0_all"

    # OTB
    mixi$mixfish_fleet[mixi$metier_in == "OTB_CRU_16-31_0_0"] <- "OTB_CRU_16-31_0_0_all"
    mixi$mixfish_fleet[mixi$metier_in == "OTB_CRU_32-69_0_0"] <- "OTB_CRU_32-69_0_0_all"
    mixi$mixfish_fleet[mixi$metier_in == "OTB_DEF_32-69_0_0"] <- "OTB_DEF_32-69_0_0_all"
    mixi$mixfish_fleet[mixi$metier_in == "OTB_MCD_70-99_0_0"] <- "OTB_CRU_70-99_0_0_all"
    mixi$mixfish_fleet[mixi$metier_in == "OTB_MCD_100-119_0_0"] <- "OTB_DEF_100-119_0_0_all"
    mixi$mixfish_fleet[mixi$metier_in == "OTB_MCD_>=120_0_0"] <- "OTB_DEF_>=120_0_0_all"

    # SDN
    mixi$mixfish_fleet[mixi$metier_in %in% c("SDN_DEF_>=120_0_0")] <- "SDN_DEF_>=120_0_0_all"
    mixi$mixfish_fleet[mixi$metier_in %in% c("SDN_DEF_100-119_0_0")] <- "SDN_DEF_100-119_0_0_all"
    #Above, not sure SDN_DEF_100-119_0_0 is a mixfish fleet in the North sea, but the code is in the vocab
    #Before these two metiers were joined in >=120

    # SSC
    mixi$mixfish_fleet[mixi$metier_in %in% c("SSC_DEF_>=120_0_0")] <- "SSC_DEF_>=120_0_0_all"
    mixi$mixfish_fleet[mixi$metier_in %in% c("SSC_DEF_100-119_0_0")] <- "SSC_DEF_100-119_0_0_all"
    #Above, not sure SDN_DEF_100-119_0_0 is a mixfish fleet in the North sea, but the code is in the vocab

    # GNS
    mixi$mixfish_fleet[mixi$metier_in == "GNS_DEF_90-99_0_0"] <- "GNS_DEF_90-99_0_0_all"
    mixi$mixfish_fleet[mixi$metier_in == "GNS_DEF_100-119_0_0"] <- "GNS_DEF_100-119_0_0_all"
    mixi$mixfish_fleet[mixi$metier_in == "GNS_DEF_120-219_0_0"] <- "GNS_DEF_120-219_0_0_all"
    mixi$mixfish_fleet[mixi$metier_in == "GNS_DEF_>=220_0_0"] <- "GNS_DEF_>=220_0_0_all"

    # LLS
    mixi$mixfish_fleet[substr(mixi$metier_in, 1, 3) == "LLS"] <- "LLS_FIF_0_0_0_all"

    # FPO
    mixi$mixfish_fleet[mixi$metier_in == "FPO_CRU_>0_0_0"] <- "FPO_CRU_0_0_0_all"

    # SPF_32-69
    mixi$mixfish_fleet[mixi$metier_in == "OTM_SPF_32-69_0_0"] <- "OTM_SPF_32-69_0_0_all"
    #Above, This is not according to the annex, since I have stolen the fleet from another area
    #In the past we would probably not have submitted this fleet, since it normally don't catch
    #stocks under WGNSSK & MIXFISH. It has been included, since we now include all effort.

    # IBC
    mixi$mixfish_fleet[mixi$metier_in %in% c("OTM_SPF_16-31_0_0",
                                             "OTB_DEF_<16_0_0",
                                             "OTB_DEF_16-31_0_0",
                                             "OTB_SPF_>=120_0_0",
                                             "OTM_SPF_>=120_0_0")] <- "MIS_MIS_0_0_0_IBC"
    #Above, data from 1987-2024. SPF_>=120_0_0 is trips mainly with 999 in mesh and catching SPF
    #OTB_SPF_>=120_0_0 & OTM_SPF_>=120_0_0 are mainly from unsorted fisheries

    # DRB_MOL
    mixi$mixfish_fleet[mixi$metier_in == "DRB_MOL_>=0_0_0"] <- "DRB_MOL_0_0_0_all"
    #Above, This is not according to the annex, since I have stolen the fleet from another area
    #In the past we would probably not have submitted this fleet, since it normally don't catch
    #stocks under WGNSSK & MIXFISH. It has been included, since we now include all effort.


    # PS
    mixi$mixfish_fleet[substr(mixi$metier_in, 1, 2) == "PS"] <- "PS"
    #Above, This is not according to the annex, since I have stolen the fleet from another AWG.
    #The fleet is not in the MIXFISH list
    #In the past we would probably not have submitted this fleet, since it normally don't catch
    #stocks under WGNSSK & MIXFISH. It has been included, since we now include all effort.

    # All other
    # mixi$mixfish_fleet[substr(mixi$metier_in, 1, 3) == "No_"] <- "MIS_MIS_0_0_0_HC"
    # mixi$mixfish_fleet[is.na(mixi$mixfish_fleet)] <- "MIS_MIS_0_0_0_HC"

  }
  mix_1 <- rbind(mix_1, mixi)
}


test_7d <-
  summarise(
    group_by(
      subset(mix_1, fao_area %in% c("27.7.d")),
      merged_metier_level6,
      metier_level6_ret,
      mixfish_fleet
    ),
    kg = sum(kg),
    trips = sum(trips)
  )

test_4 <-
  summarise(
    group_by(
      subset(mix_1, fao_area %in% c("27.4.a", "27.4.b", "27.4.c")),
      merged_metier_level6,
      metier_level6_ret,
      mixfish_fleet
    ),
    kg = sum(kg),
    trips = sum(trips)
  )

# 
# test <-
#   distinct(filter(mix, fao_area %in% c("27.3.a.20", "27.3.a.21")),
#            metier_level6_ret,
#            mixfish_fleet)
# test_2 <-
#   distinct(filter(
#     mix,
#     fao_area %in% c("27.4.a", "27.4.b", "27.4.c", "27.7.d", "27.6.a")
#   ),
#   metier_level6_ret,
#   mixfish_fleet)

# 
# area_7d <-
#   summarise(group_by(filter(mix_1, fao_area %in% c("27.7.d")),
#            metier_level6_ret,
#            mixfish_fleet),
#            kg = sum(kg),
#            trips = sum(trips)
#   )
# 
# area_4 <-
#   arrange(summarise(group_by(filter(mix_1, fao_area %in% c("27.4.a", "27.4.b", "27.4.c")),
#            metier_level6_ret,
#            mixfish_fleet),
#            kg = sum(kg),
#            trips = sum(trips)
#   ), -kg)
# 
# area_4$pct_cum <- cumsum(area_4$kg)*100/sum(area_4$kg)

fleet <- mix_1

# rm(mix, mix_1)
```


```{r output, include = T}

matrix_out <-
  distinct(
    ungroup(fleet),
    fao_area,
    metier_level6_ret,
    # obs_at_sea_fleets_no_gns,
    # obs_at_sea_fleets_gns,
    # merged_metier_level6,
    mixfish_fleet
  )

matrix_out

# matrix_out <- rename(matrix_out, metier_level6 = metier_level6_ret)

saveRDS(matrix_out, paste0(path_out, filename_out, ".rds"))
write.csv(matrix_out, paste0(path_out, filename_out, ".csv"), row.names = F)

```


