---
title: "Fleet, reference table, documentation"
author: "Kirsten Birch Håkansson, DTU Aqua"
date: "\today"
output:
  html_document:
    toc: true
---

```{r setup, include = F}

knitr::opts_chunk$set(echo = TRUE, message = F, warnings = F)

options(scipen = 999)

path_out <- "Q:/mynd/SAS Library/fleet/analyses/area_4/" 
filename_out <- "area_4"

options(scipen = 999)

library(dplyr)

years <- c(1987:2024)


```

# Data
Pick all trips with some landings from area 27.7.d

Mixfish Species
ANF (Lophius spp.)
ANK (Lophius budegassa)
BLL (Scophthalmus rhombus)
CAA (Anarhichas lupus)
COD (Gadus morhua)
COE (Conger conger)
DAB (Limanda limanda)
FLE (Platichthys flesus)
GUG (Eutrigla gurnardus)
GUR (Aspitrigla cuculus)
HAD (Melanogrammus aeglefinus)
HAL (Hippoglossus hippoglossus)
HER (Clupea harengus)
HKE (Merluccius merluccius)
HOM (Trachurus trachurus)
LDB (Lepidorhombus boscii)
LEM (Microstomus kitt)
LEZ (Lepidorhombus spp.)
LIN (Molva molva)
MAC (Scomber scombrus)
MEG (Lepidorhombus whiffiagonis)
MON (Lophius piscatorius)
NEP (Nephrops norvegicus) *** Note: Please also indicate the FU code here, i.e. NEP.FU.16, see "DC_Annex_WGMIXFISH2 Catch and Effort template" for more details.
NOP (Trisopterus esmarkii)
PLE (Pleuronectes platessa)
POK (Pollachius virens)
POL (Pollachius pollachius)
RJU (Raja undulata)
SKA (aggregated rays and skates: RJC, SKA, RAJ, RJA, RJB, RJC, RJE, RJF, RJH, RJI, RJM, RJN, RJO, RJR, SKX, SRX)
SDV (aggregated dogfish: DGS, DGH, DGX, DGZ, SDV)
SOL (Solea solea)
SPR (Sprattus sprattus)
TUR (Scophthalmus maximus)
WHB (Micromesistius poutassou)
WHG (Merlangius merlangus)
All remaining species should be aggregated under 'OTH'.


```{r data}

dat <- readRDS("Q:/mynd/SAS Library/fleet/analyses/area_4/data_area_4.rds")

ind_spp <- c("BRS", "BLH", "TBS", "PIL", "ANS", "HMK", "SPE", "ARG", "SIL", "MAK", "BMS")

spp_mixfish <- c("HAT", "SLH", "TOR", "ISG", "SKR", "KUL", "KLM", "RTG", "DVH", "RSP", "MSJ", "LSJ", "TNG", "PHG", "HVL")

#"SIL", "SPE"

```

# Diff old and new metiers
```{r}



```


# OTB_SPF_>=120_0_0
```{r}

test_all <- subset(dat, metier_level6_ret == "OTB_SPF_>=120_0_0")

test_all <-
  arrange(test_all, -kg)
test_all$pct_cum <- cumsum(test_all$kg)*100/sum(test_all$kg)

knitr::kable(arrange(summarise(group_by(test_all, art), kg = sum(kg)), -kg))


test_huc <- subset(dat, metier_level6_ret == "OTB_SPF_>=120_0_0" & !(art %in% ind_spp))

test_huc <-
  arrange(test_huc, -kg)
test_huc$pct_cum <- cumsum(test_huc$kg)*100/sum(test_huc$kg)


knitr::kable(arrange(summarise(group_by(test_huc, art), kg = sum(kg)), -kg))

```


# OTM_SPF_>=120_0_0
```{r}

test_all <- subset(dat, metier_level6_ret == "OTM_SPF_>=120_0_0")

test_all <-
  arrange(test_all, -kg)
test_all$pct_cum <- cumsum(test_all$kg)*100/sum(test_all$kg)

knitr::kable(arrange(summarise(group_by(test_all, art), kg = sum(kg)), -kg))


test_huc <- subset(dat, metier_level6_ret == "OTM_SPF_>=120_0_0" & !(art %in% ind_spp))

test_huc <-
  arrange(test_huc, -kg)
test_huc$pct_cum <- cumsum(test_huc$kg)*100/sum(test_huc$kg)


knitr::kable(arrange(summarise(group_by(test_huc, art), kg = sum(kg)), -kg))

```

# No_Matrix6

```{r}
test_all <- subset(dat, metier_level6_ret == "No_Matrix6")

test_all <-
  arrange(test_all, -kg)
test_all$pct_cum <- cumsum(test_all$kg)*100/sum(test_all$kg)

knitr::kable(arrange(summarise(group_by(test_all, art), kg = sum(kg)), -kg))


test_huc <- subset(dat, metier_level6_ret == "OTM_SPF_>=120_0_0" & !(art %in% ind_spp))

test_huc <-
  arrange(test_huc, -kg)
test_huc$pct_cum <- cumsum(test_huc$kg)*100/sum(test_huc$kg)


knitr::kable(arrange(summarise(group_by(test_huc, art), kg = sum(kg)), -kg))
```

# OTM_DEF_32-69_0_0
```{r}
test_all <- subset(dat, metier_level6_ret == "OTM_DEF_32-69_0_0")
test_all <-
  arrange(test_all, -kg)
test_all$pct_cum <- cumsum(test_all$kg)*100/sum(test_all$kg)

knitr::kable(arrange(summarise(group_by(test_all, art), kg = sum(kg)), -kg))


test_huc <- subset(dat, metier_level6_ret == "OTM_SPF_>=120_0_0" & !(art %in% ind_spp))

test_huc <-
  arrange(test_huc, -kg)
test_huc$pct_cum <- cumsum(test_huc$kg)*100/sum(test_huc$kg)


knitr::kable(arrange(summarise(group_by(test_huc, art), kg = sum(kg)), -kg))
```


# Test metier relation

```{r}

fleet_old <- readRDS("Q:/mynd/SAS Library/fleet/fleet_old_metiers.rds")

dat_4 <- subset(dat, substr(fao_area, 1, 5) == "27.4.")

dat_1 <- left_join(dat_4, fleet_old, by = c("fao_area" = "fao_area", "metier_level6_ret" = "metier_level6_ret"))

area_4_all <-
  arrange(summarise(group_by(filter(dat_1, fao_area %in% c("27.4.a", "27.4.b", "27.4.c")),
           metier_level6_ret,
           mixfish_fleet),
           kg = sum(kg),
           trips = sum(trips)
  ), -kg)

area_4_all$pct_cum <- cumsum(area_4_all$kg)*100/sum(area_4_all$kg)


dat_1 <- left_join(dat_4, fleet_old, by = c("fao_area" = "fao_area", "metier_level6_ret" = "metier_level6_ret"))

area_4_huc_dat <- subset(dat_1, fao_area %in% c("27.4.a", "27.4.b", "27.4.c") & (art %in% spp_mixfish) & year > 2023)

area_4_huc <-
  arrange(summarise(group_by(filter(dat_1, fao_area %in% c("27.4.a", "27.4.b", "27.4.c") & (art %in% spp_mixfish) & year > 2023),
           metier_level6_ret,
           mixfish_fleet, 
           metier_level_6_new,
           metier_level_6_new_mrk),
           kg = sum(kg),
           trips = length(unique(match_alle))
  ), -kg)

area_4_huc$pct_cum <- cumsum(area_4_huc$kg)*100/sum(area_4_huc$kg)

```

